---
title: "Rmarkdown Arrival Distribution Analysis"
author: "Rita Brodesky,Ido Nahamni, Ofri Fox"
date: "6 6 2022"
output:
  word_document: default
  html_document: default
---
we will need the following libraries: fitdistrplus, magrittr

```{r libraries, include=TRUE,echo=TRUE}
library(fitdistrplus)
library(magrittr)
```

## R Markdown
First we will load the data:

```{r}
filePath=choose.files()
table <-read.csv(filePath,header=T)

arrivalTimes <- subset(table[2:50,3:4]) #gets the data from the excel

cizitensGap <- arrivalTimes[,1] #The gaps between the arrival times of citizens
soldiersGap <- arrivalTimes[,2] #The gaps between the arrival times of soldiers
```


At first we will  look at the data and understand - the data range, continous,
are there any outliers? 
For that we can use the following plots:

```{r empirical plots}
par(mfrow=c(1,3)) # plot of citizen 
plot(cizitensGap,ylab="Sample values") # plot ( left graph )
hist(cizitensGap, prob=TRUE)
lines(density(cizitensGap), col = "hotpink", lwd = 3)


par(mfrow=c(1,3)) # plot of soldiers 
plot(soldiersGap,ylab="Sample values") # plot ( left graph )
hist(soldiersGap, prob=TRUE)
lines(density(soldiersGap), col = "hotpink", lwd = 3)

```
 From the plot we can see that there is no outluries, furthermore we can 
 see a clear shape of normal or exponential distriution in the hisrogram.
 due to we will try to fit a normal and exponential distribution to  our data.

for citizen 

```{r}
 citizensExpFit <- fitdist(cizitensGap, distr = "exp")
 citizensunifFit <- fitdist(cizitensGap, distr = "unif")

 citiznesNormFit <- fitdist(cizitensGap, distr = "norm")
 summary(citizensExpFit)
 summary(citiznesNormFit)

```

for soldiers
```{r}

 soldiersExpFit <- fitdist(soldiersGap, distr = "exp")
 soldiersNormFit <- fitdist(soldiersGap, distr = "norm")
 summary(soldiersExpFit)
 summary(soldiersNormFit)

```
Comparing the maximum likelihood of the normal and exponential distribution, we can 
see that both the aic and bic are lower in the exponential threrefore we will say 
that the exponential distribution are more fittted to our data.
we can see that the maximum likelihood Parameter is -67.10704 for the citizen and -81.68311 for the soldiers.


```{r}

citiznesExpGof<- gofstat(citizensExpFit)%>%print()
citiznesExpGof$kstest%>%print()

soldiersExpGof<- gofstat(soldiersExpFit)%>%print()
soldiersExpGof$kstest%>%print()

```
we executed KS test and we can see that we will not reject H0.


